A semantics of core AUTOSAR

### 2016-08-25 paper/paper.tex
Paper updates

@@

@@

Axioms (13) and (15) define unbuffered inter-process communication from a runnable instance point of view. These transitions are just syntactic variants of shared variable reading and writing (axioms (5) and (7)). A data element (\textbf{delem}) process term contains two pieces of state in addition to its address: a communicated data value and a boolean flag for keeping track of unread writes. Axioms (14) and (16) capture reads and writes to the data value and also set the update flag accordingly. The side-condition in axiom (16) makes the rule apply only if there is a static connection from the data element being written and the address of the matched term (recall that data element storage is associated with the receiving side of a connection). Because AUTOSAR allows sender-receiver communication patterns such that $\Tconnect {i.p.e} a$ and $\Tconnect {i.p.e} b$ are simultaneously true, parallel data element updates like the following are possible:
$$
\begin{array}{c}
  \Trinst {i.r} c \Xs {\TrteWrite {p.e} v k} \,\Opar  \\
  {\Tdelem a \_ \_} \Opar {\Tdelem b \_ \_} \vspace{0.6ex} \\
  \red{\say{i.p.e}{\Twr v}} \\
  \Trinst {i.r} c \Xs {\Tap k \Tvoid} \,\Opar \\
  {\Tdelem a \Ttrue v} \Opar {\Tdelem b \Ttrue v}
\end{array}
$$
As an aside, note that the associativity of the parallel composition operator is made entirely irrelevant by the symmetric shape of transition rules (1) and (2).

>>>>

TODO: Perhaps match up the order of introducing the terms of the initial process term \V{P_0} with these subsections

@@

TODO: Dangling pointer to Section~\ref{sect:DiscExcl}

@@

Axioms (13) and (15) define unbuffered inter-process communication from a runnable instance point of view. These transitions are just syntactic variants of shared variable reading and writing (axioms (5) and (7)). A data element (\textbf{delem}) process term contains two pieces of state in addition to its address: a communicated data value and a boolean flag for keeping track of unread writes. Axioms (14) and (16) capture reads and writes to the data value and also set the update flag accordingly. The side-condition in axiom (16) makes the rule apply only if there is a static connection from the data element being written and the address of the matched term (recall that data element storage is associated with the receiving side of a connection). Because AUTOSAR allows sender-receiver communication patterns to be one-to-many (such as $\Tconnect {i.p.e} a$ and $\Tconnect {i.p.e} b$), parallel data element updates like the following are possible:
$$
\begin{array}{c}
  \Trinst {i.r} c \Xs {\TrteWrite {p.e} v k} \,\Opar  \\
  {\Tdelem a \_ \_} \Opar {\Tdelem b \_ \_} \vspace{0.6ex} \\
  \red{\say{i.p.e}{\Twr v}} \\
  \Trinst {i.r} c \Xs {\Tap k \Tvoid} \,\Opar \\
  {\Tdelem a \Ttrue v} \Opar {\Tdelem b \Ttrue v}
\end{array}
$$
As an aside, note that the associativity of the parallel composition operator is made entirely irrelevant by the symmetric shape of transition rules (1) and (2).

TODO: ? I don't get that aside ? (associativity is about equality of terms: (a|b)|c == a|(b|c) but the rules deal with transitions, not equality.)
